---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file and run
`devtools::build_readme()` -->
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# UKgeogRaphies
<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![R-CMD-check](https://github.com/WarwickCIM/ukgeographies/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/WarwickCIM/ukgeographies/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

> [!WARNING]  
> This package is highly experimental and is still a WIP. Expect uncomplete 
> features, frequent breaks, lack of documentation and changes in the API.


> ### Because UK Geographies are complex enough[^complex], working with them should be easy enough.

The goal of `{UKgeogRaphies}` is to provide an interface to easily retrieve
geospatial data from ONS' Geoportal and make it usable within R. 

So far it provides very limited functionality to download boundaries in the UK
and convert them to `sf` objects.

**Acknowledgement**: this packages is highly inspired (feature wise) by 
[`{UKgeog}`](https://l-hodge.github.io/ukgeog/), which ceased to work after ONS 
changed their API and has not been maintained since 2022.


## Installation

You can install the development version of ukgeographies from
[GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("WarwickCIM/ukgeographies")
```

## Getting geographical boundaries

So far, this package provides two functions to download a selected boundary from ONS geoportal and convert it into a `sf` object: `boundaries_get()` and `boundaries_select()`

`boundaries_get()` will construct the API query to download the desired boundary based on the parameters.

```{r example}
library(ukgeographies)

# Get a sf object from 
countries_2023 <- boundaries_get("CTRY", 2023, "BUC")

class(countries_2023)

countries_2023

plot(countries_2023["CTRY23NM"])
```


Because not every boundary is available for every year or detail level, some combination of parameters may yield invalid queries. To address that issue, `boundaries_select()` provides an interface that exposes the available options based on the previous selection, so the combination will always be valid.

![](vignettes/media/boundaries_select_demo.webm)


## Boundaries

```{r echo=FALSE}
library(dplyr)
library(knitr)

ons_boundaries |> 
  select(boundary_type, boundary, detail_level, year) |> 
  group_by(boundary_type, boundary, detail_level) |> 
  arrange(year) |> 
  unique() |> 
  summarize(year = stringr::str_c(year, collapse = "; "), .groups = "drop") |> 
  arrange(boundary_type, boundary) |> 
  tidyr::pivot_wider(values_from = year, names_from = detail_level) |> 
  kable()
  
```


[^complex]: To get you started, ONS has edited a [A Beginner’s Guide to UK Geography](https://geoportal.statistics.gov.uk/datasets/c0db0e8c67d04935bcf1749ca6027fef/about) which _only_ has 137 pages.
