---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file and run
`devtools::build_readme()` -->
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# UKgeogRaphies
<!-- badges: start -->
[![R-CMD-check](https://github.com/WarwickCIM/ukgeographies/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/WarwickCIM/ukgeographies/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

> [!WARNING]  
> This package is highly experimental and is still a WIP. Expect uncomplete 
> features, frequent breaks, lack of documentation and changes in the API.


> Because UK Geographies are complex enough[^complex], working with them should be easy
enough.

The goal of `{UKgeogRaphies}` is to provide an interface to easily retrieve
geospatial data from ONS' Geoportal and make it usable within R. 

So far it provides very limited functionality to download boundaries in the UK
and convert them to `sf` objects.

**Acknowledgement**: this packages is highly inspired (feature wise) by 
[`{UKgeog}`](https://l-hodge.github.io/ukgeog/), which ceased to work after ONS 
changed their API and has not been maintained since 2022.


## Installation

You can install the development version of ukgeographies from
[GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("WarwickCIM/ukgeographies")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(ukgeographies)

# Get a sf object from 
countries_2023 <- boundaries_get("CTRY", 2023, "BUC")

class(countries_2023)

countries_2023

plot(countries_2023["CTRY23NM"])
```

[^complex]: ONS has a 
