---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# UKgeogRaphies

<!-- badges: start -->
[![R-CMD-check](https://github.com/WarwickCIM/ukgeographies/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/WarwickCIM/ukgeographies/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

This is still a WIP.

The goal of UKgeogRaphies is to retrieve geospatial data from ONS' Geoportal and
make it usable within R.

So far it provides very limited functionality to download boundaries in the UK
and convert them to `sf` objects.

## Installation

You can install the development version of ukgeographies from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("WarwickCIM/ukgeographies")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(ukgeographies)
## basic example code

countries_2022 <- get_boundaries("countries", 2022, "BUC")

class(countries_2022)

countries_2022

plot(countries_2022["CTRY22NM"])
```


You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.
