---
title: "ukgeographies"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ukgeographies)
```

## Notes on URL patterns:

-   Countries
    -   Countries (December 2022) Boundaries GB BUC: <https://services1.arcgis.com/ESMARspQHYMw9BZ9/arcgis/rest/services/Countries_December_2022_GB_BUC/FeatureServer/0/query?outFields=*&where=1%3D1&f=geojson>
    -   Countries (December 2019) Boundaries GB BUC: <https://services1.arcgis.com/ESMARspQHYMw9BZ9/arcgis/rest/services/Countries_Dec_2019_UGCB_GB_2022/FeatureServer/0/query?outFields=*&where=1%3D1&f=geojson>
-   Counties
    -   Counties (December 2021) Boundaries EN BGC : <https://services1.arcgis.com/ESMARspQHYMw9BZ9/arcgis/rest/services/Counties_December_2021_EN_BGC_2022/FeatureServer/0/query?outFields=*&where=1%3D1&f=geojson>
    -   Counties (December 2021) Boundaries EN BFC <https://services1.arcgis.com/ESMARspQHYMw9BZ9/arcgis/rest/services/Counties_December_2021_EN_BFC_2022/FeatureServer/0/query?outFields=*&where=1%3D1&f=geojson>
    -   Counties (May 2023) Boundaries EN BFC: <https://services1.arcgis.com/ESMARspQHYMw9BZ9/arcgis/rest/services/Counties_May_2023_Boundaries_EN_BFC/FeatureServer/0/query?outFields=*&where=1%3D1&f=geojson>
-   Combined authorities
    -   [Combined Authorities (December 2022) Boundaries EN BUC](https://geoportal.statistics.gov.uk/maps/f147c03bdd914124ad36fd6684358d65) :\
        <https://services1.arcgis.com/ESMARspQHYMw9BZ9/arcgis/rest/services/Combined_Authorities_December_2022_EN_BUC/FeatureServer/0/query?outFields=*&where=1%3D1&f=geojson>
    -   Countries (December 2019) Boundaries GB BUC:

Another option could be having a dataframe with all the possible URLs and retrieve them from there

### Components

Clipping / Resolution:

-   BFC: Full resolution - clipped to the coastline (Mean High Water mark)
-   BFE: Full resolution - extent of the realm (usually this is the Mean Low Water mark but, in some cases, boundaries extend beyond this to include offshore islands)
-   BGC: Generalised (20m) - clipped to the coastline (Mean High Water mark)
-   BUC: Ultra Generalised (500m) - clipped to the coastline (Mean High Water mark)

```{r eval=FALSE, include=FALSE}
path <- paste0("https://services1.arcgis.com/ESMARspQHYMw9BZ9/arcgis/rest/services/",
               object, 
               "_",
               month, # Create a function to induce the month if URL does not exist
               "_", year, "_", 
               region, # England, Wales, Scotland...
               "_", 
               resolution,
               "/FeatureServer/0/query?outFields=*&where=1%3D1&f=geojson")
```
